Incentivizing Exploration with Unbiased History

### 2018-11-01 2level.tex
Rewrote the 2level/warmup section.

%!TEX root = main.tex
\section{Warm-up:  2-Level Explore-then-Exploit Policy}
\swedit{Now we provide a simple policy that can incentivize the agents
  to perform non-adaptive exploration and achieve a regret rate of
  $\tilde O(T^{2/3})$. The policy essentially follows the
  ``explore-then-exploit'' paradigm and consists of two phases, which can
  be described as a two-level information graph (as shown in
  Figure~\ref{fig:2level}).  In the first level, we perform
  exploration by simulating $T_1$ independent runs of \ALGG of $\GdT$
  rounds. This is done by dividing the first $T_1 \cdot \GdT$
  agents into $T_1$ groups of equal size and allowing each agent to only observe
  the history of all previous agents in the same group.  In the second
  level, we ``exploit'' by showing all the remaining agents the entire
  history of first phase.

  The key idea behind the policy is that the first level effectively
  boosts the exploration probability of \ALGG. Since each run of
  \ALGG explores all arms with constant probability (Lemma
  \ref{lem:greedy}), by simulating multiple runs of \ALGG, we can
  ensure that with high probability, every arm is pulled a
  sufficient number of times. The below lemma follows from
  concentration bounds.

} \nicomment{there was a proof of this once; i remember checking it. if it still exists, let's throw it in an appendix.}

@@

\iffalse
The 2-level recommendation policy is constructed as following.
In the first level, we run $T_1$ \ALGG of $\GdT$ rounds ``in parallel''. More specifically, we divide the first $T_1 \cdot \GdT$ agents into $T_1$ groups of equal size and agents only observe the history of all previous agents in the same group.
In the second level, we show the rest $T-T_1\cdot \GdT$ agents the history of first $T_1 \cdot \GdT$ rounds. We will pick $T_1$ in Theorem \ref{thm:2level}. 
See also Figure \ref{fig:2level} for a graphical view of the information flow.

The idea of this 2-level recommendation policy is simple. We first try to explore all arms enough amount of times in the first level using multiple runs of \ALGG under the guarantee of Lemma \ref{lem:greedy}. After that, by concentration argument, we can show that while observing the history of the first level, agents in the second level pick an arm with mean close to the best arm's mean. 
\fi

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=blue!20!white]
 (0,2)--(10,2)--(10,3)--(0,3)--cycle;
  \filldraw[fill=red!20!white]
  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
  \draw (0.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
  \draw (1.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
  \draw(2.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
  \draw(3.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
  \draw(9.5,1)--(5,2);
  \node at(5,0.5){$\cdots$};
  \node at(6,0.5){$\cdots$};
  \node at(7,0.5){$\cdots$};
  \node at(8,0.5){$\cdots$};
  \node at(5,2.5){$T -T_1 \cdot \GdT$};
  \node at(0.5,0.5){$\GdT$};
  \node at(1.5,0.5){$\GdT$};
  \node at(2.5,0.5){$\GdT$};
  \node at(3.5,0.5){$\GdT$};
  \node at(9.5,0.5){$\GdT$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \draw[->] (11,0)--(11,3);
  \node at(11.5,1.5)[ rotate=90]{Time};

  \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (10,-0.2) -- (0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ runs of \ALGG in parallel};
\end{tikzpicture}

\caption{Structure of information graph for the 2-level policy. Each
  red ``box'' in level 1 corresponds to a path connecting a set of
  $T_G$ agents. The entire history in level 1 is then aggregated and
  shown to each agent in level 2.}
\label{fig:2level}
\end{figure}

\swedit{As a result, every agent in the second level will pull an arm
  with mean reward close to the optimal, which gives us the following
  regret guarantee.}

\begin{theorem}
\label{thm:2level}
By setting $T_1 = T^{2/3}\log(T)^{1/3}$, the 2-level policy gets
expected regret $O(T^{2/3} \log(T)^{1/3})$.
\end{theorem}

\swcomment{I think this proof should go to appendix, so I didn't do
  too much refactoring} \nicomment{I read this last week and talked to jieming about it; seemed right but a bit messy, but since it's going in an appendix i won't re-read/edit it now.}

\begin{proof}
  We will set $T_1$ later in the proof, depending on whether the gap
  parameter $\Delta$ is known. For now, we just need to know we will
  make $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$. Since this policy is
  agnostic to the indices of the arms, we assume w.l.o.g. that arm 1
  has the highest mean.

  The first $T_1 \cdot \GdT$ rounds will get total regret at most
  $T_1 \cdot \GdT$.  We focus on bounding the regret from the second
  level of $T - T_1 \cdot \GdT$ rounds. We consider the following two
   events. We will first bound the probability that both of them
  happen and then we will show that they together imply upper bounds
  on $|\hat{\mu}^t_a - \mu_a|$'s for any agent $t$ in the second
  level. Recall $\hat{\mu}^t_a$ is the estimated mean of arm $a$ by
  agent $t$ and agent $t$ picks the arm with the highest
  $\hat{\mu}^t_a$.

% \begin{itemize}
  \OMIT{\paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
  Define $W_1^a$ to be the event that the number of arm $a$ pulls in
  the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
  \swedit{As long as we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$,
    this implies that the number of arm $a$ pulls is then at least
    $q_a T_1/2$.} 
\OMIT{  By Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
}
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By Lemma~\ref{lem:t1runs}, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\OMIT{\paragraph{Concentration of the empirical mean of arm $a$ pulls
    in the first level.}}  Next, we show that the empirical mean of
each arm $a$ is close to the true mean. To facilitate our reasoning,
let us imagine there is a tape of length $T$ for each arm $a$, with
each cell containing an independent draw of the realized reward from
the distribution $\cD_a$. Then for each arm $a$ and any $N\in [T]$, we
can think of the sequence of the first $N$ realized rewards of $a$
coming from the prefix of $N$ cells in its reward tape. Define
$W^{a,t}_2$ to be the event that the empirical mean of the first $t$
\swedit{realized rewards in the tape} of arm $a$ is at most
$\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be the
intersection of these events (i.e.  $\bigcap_{a,t} W^{a,t}_2$).  By
Chernoff bound,\swcomment{$t$ may be confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound, 
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]

By union bound, we know $\Pr[W_1 \cap W_2] \geq 1 - 3/T$. For the
remainder of the analysis, we will condition on the event
$W_1 \cap W_2$.

For any arm $a$ and agent $t$ in the second level, by $W_1$ and $W_2$, we have
\[
|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}.
\]
By $W_1$ and Assumption \ref{ass:embehave}, we have
\[
|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{c_m}{\sqrt{q_aT_1/2}}.
\]
Therefore,
\[
|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}+\frac{c_m}{\sqrt{q_aT_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total expected regret is at most 
\[
T_1 \cdot \GdT + T \cdot (1-\Pr[W_1 \cap W_2]) + T \cdot  6 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get expected regret $O(T^{2/3}\log(T)^{1/3})$.
\OMIT{Notice that if we know the gap parameter is known to be larger than
$\Delta$, we can set
\[
T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
\]
In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
\]
This completes the proof.}
\end{proof}

\begin{remark}
  If the gap parameter $\Delta$ is known to the principal, we can set
  $$T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2
      \cdot p_G} \log(T) \right),$$ and achieve an expected regret of
  $O(\log(T) \cdot \Delta^{-2})$.
\end{remark}

>>>>

%!TEX root = main.tex
\section{Warm-up: full-disclosure paths}

We first consider a disclosure policy that reveals the full history in each round $t$, \ie $m_t=\SubH{t-1}$; we call it the \emph{full-disclosure policy}. The info-path for this policy is a simple path. We use this policy as a ``gadget" in our constructions. Hence, we formulate it slightly more generally:

\begin{definition}
A subset of rounds $S\subset [T]$ is called a \emph{full-disclosure path} in the  info-graph $G$ if the induced subgraph $G_S$ is a simple path, and it connects to the rest of the graph only through the terminal node $\max(S)$, if at all.
\end{definition}

We prove that for a constant number of arms, with constant probability, a full-disclosure path of constant length suffices to sample each arm at least once. We will build on this fact throughout.

\begin{lemma}\label{lem:greedy}
There exist numbers $\GdT>0$ and $\GdP>0$ that depend only on $K$, the number of arms, with the following property. Consider an arbitrary disclosure policy, and let $S\subset [T]$ be a full-disclosure path in its info-graph, of length $|S|\geq \GdT$. Under Assumption \ref{ass:embehave}, with probability at least $\GdP$, subhistory $\SubH{S}$ contains at least once sample of each arm $a$.
\end{lemma}

\begin{proof}[Proof Sketch]
\end{proof}

\ascomment{Where do we need to introduce the expected \#pulls in full-disclosure path?}

We provide a simple disclosure policy based on full-disclosure paths. The policy follows the ``explore-then-exploit'' paradigm. The ``exploration phase" comprises the first $N = T_1\cdot \GdT$ rounds, and consists of $T_1$ full-disclosure paths of length $\GdT$ each. Here $\GdT$ is the constant from Lemma~\ref{lem:greedy}, and $T_1$ is a parameter. In the ``exploitation phase", each agent $t>N$ receives the full subhistory from exploration, \ie $m_t = \SubH{[N]}$. The info-graph for this disclosure policy is shown in Figure~\ref{fig:2level}.

\begin{figure}[H]
\centering
\begin{tikzpicture}
 \filldraw[fill=blue!20!white]
 (0,2)--(10,2)--(10,3)--(0,3)--cycle;
  \filldraw[fill=red!20!white]
  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
  \draw (0.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
  \draw (1.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
  \draw(2.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
  \draw(3.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
  \draw(9.5,1)--(5,2);
  \node at(5,0.5){$\cdots$};
  \node at(6,0.5){$\cdots$};
  \node at(7,0.5){$\cdots$};
  \node at(8,0.5){$\cdots$};
  \node at(5,2.5){$T -T_1 \cdot \GdT$ rounds};
  \node at(0.5,0.5){$\GdT$};
  \node at(1.5,0.5){$\GdT$};
  \node at(2.5,0.5){$\GdT$};
  \node at(3.5,0.5){$\GdT$};
  \node at(9.5,0.5){$\GdT$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \draw[->] (11,0)--(11,3);
  \node at(11.5,1.5)[ rotate=90]{Time};

  \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (10,-0.2) -- (0,-0.2) node [black,midway,yshift=-0.6cm] 
  {$T_1$ full-disclosure paths of length $\GdT$ each};
\end{tikzpicture}

\caption{Info-graph for the 2-level policy. }
%Each red box in level 1 corresponds to a path connecting a set of
%  $T_G$ agents. The entire history in level 1 is then aggregated and
%  shown to each agent in level 2.}
\label{fig:2level}
\end{figure}

It is useful to think of the info-graph as having two levels (corresponding to exploration and exploitation). Accordingly, we call this policy the \emph{2-level policy}. We show that it incentivizes the agents to perform non-adaptive exploration, and achieves a regret rate of  $\tilde O_K(T^{2/3})$. The key idea is that using many full-disclosure paths ``in parallel" ensures that sufficiently many samples of each arm are collected during exploration.

\begin{theorem}\label{thm:2level}
The 2-level policy with parameter $T_1 = T^{2/3}\,\log(T)^{1/3}$ achieves regret
\[ \reg(T) \leq O_K\left( T^{2/3}\, \log(T)^{1/3} \right).\]
\end{theorem}

\begin{remark}
For a constant $K$, the number of arms, we match the optimal regret rate for non-adaptive multi-armed bandit algorithms. If the gap parameter $\Delta$ is known to the principal, then (for an appropriate tuning of parameter $T_1$) we can achieve regret 
  $\reg(T) \leq O_K(\log(T) \cdot \Delta^{-2})$.
\end{remark}

@@
